Millions of Type Errors

### 2023-09-11 programming23/paper.tex
Use BibTeX rather than biber
General tidying up
CCS classification

%% BEGIN tobias pape 2021-11-06
\makeatletter
\newcommand*\abstractpart[1]{\unskip\par\noindent{\firamedium\color{P@GrayFG}{#1}}\enspace}
\makeatother
%% END

\usepackage{alltt}
\usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

\addbibresource{bib.bib}

@@

\author[a]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) is a postdoc at Brown University. He will be joining the University of Utah in Fall~2023.}
\affiliation[a]{Brown University, Providence, RI, USA}
% \orcid{0000-0001-7078-9287}
\affiliation[a]{Brown University, Providence, RI, USA}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011039.10011311</concept_id>
<concept_desc>Software and its engineering~Semantics</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011024.10011032</concept_id>
<concept_desc>Software and its engineering~Constraints</concept_desc>
<concept_significance>100</concept_significance>
</concept>
<concept>
<concept_id>10011007.10011006.10011008.10011009.10011012</concept_id>
<concept_desc>Software and its engineering~Functional languages</concept_desc>
<concept_significance>100</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Semantics}
\ccsdesc[100]{Software and its engineering~Constraints}
\ccsdesc[100]{Software and its engineering~Functional languages}

@@

{ \printbibliography }

>>>>

%% BEGIN tobias pape 2021-11-06
% Why do we need this?
%\makeatletter
%\newcommand*\abstractpart[1]{\unskip\par\noindent{\firamedium\color{P@GrayFG}{#1}}\enspace}
%\makeatother
%% END

\usepackage{alltt}
% Not sure why <Programming> is recommending non-standard tools
% \usepackage[backend=biber]{biblatex}
\usepackage{amssymb}
\usepackage{calc}
\usepackage{colortbl}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
% Errors with
% ! Undefined control sequence.
% <argument> \l__siunitx_number_implicit_plus_bool 
% l.61 \begin{document}
% using Mac TeXlive 20230313_2
% \usepackage{siunitx}
\usepackage{tikz}
\usepackage{subcaption}
\usepackage{wasysym}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\author[a]{Ben Greenman}
\authorinfo{(\email{benjamin.l.greenman@gmail.com}) is a postdoc at Brown University. He will be joining the University of Utah in Fall~2023.}
\affiliation[a]{Brown University, Providence, RI, USA}
% \orcid{0000-0001-7078-9287}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002944.10011123.10010916</concept_id>
<concept_desc>General and reference~Measurement</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{General and reference~Measurement}

@@

\bibliography{bib}
